Errorless irrationality: removing error-driven components from the inverse base-rate effect paradigm

### 2023-01-09 docs/manuscript.tex
work on experiment 2 method and results

\begin{table}[ht]
  \begin{center}
    \caption{Group-level mean probabilities for each stimulus presented during the test phase in Experiment 1. \\}
    \label{tab:results-exp1}
    \vskip 0.12in
    \begin{tabular}{rcc}
      \hline
      & $P(common)$ & $P(rare)$ \\
      \hline
      A & 0.69 & 0.31 \\
      AB & 0.94 & 0.06 \\
      AC & 0.08 & 0.92 \\
      B & 0.94 & 0.06 \\
      \textbf{BC} & \textbf{0.33} & \textbf{0.67} \\
      C & 0.04 & 0.96 \\
    \end{tabular}
  \end{center}
\end{table}

@@

In this experiment, we implemented the IBRE in a way most similar to cued-recall memory tasks.
Previous category labels were treated as features.
And features were selected to be solid black geometric shapes.
The task asked participants to memorise the arrangement of these shapes.
On each trial, we randomised the position of the geometric shapes in the arrangement.
This further minimised the chances of having any design component suggesting which feature is the category label.

@@

\begin{figure}
  \begin{center}
    \caption{Stuff.}
    \label{figure:exp2-stimuli}
    \includegraphics[scale=0.15]{figures/experiment_2_stimuli.pdf}
  \end{center}
\end{figure}

@@

@@

30 made it into the analysis

\begin{table}[H]
  \begin{center}
    \caption{Caption.\\}
    \label{tab:results-exp2}
    \vskip 0.12in
    \begin{tabular}{rcc}
      \hline
       & $P(common)$ & $P(rare)$ \\
      \hline
      A & 0.78 & 0.22  \\
      AB & 0.95 & 0.05 \\
      AC & 0.09 & 0.91 \\
      B & 0.92 & 0.07  \\
      \textbf{BC} & \textbf{0.35} & \textbf{0.65} \\
      C & 0.08 & 0.92 \\
    \end{tabular}
  \end{center}
\end{table}

$M = 0.64$, 95\% HDI $[0.53, 0.75]$, $\mathrm{BF}_{10} = 4.09$

@@

\section{Acknowledgments}

In the \textbf{initial submission}, please \textbf{do not include
  acknowledgments}, to preserve anonymity.  In the \textbf{final submission},
place acknowledgments (including funding information) in a section \textbf{at
the end of the paper}.

>>>>

\begin{table}[ht]
  \begin{center}
    \caption{Group-level mean probabilities for each stimulus presented during the test phase in Experiment 1 after exclusion. \\}
    \label{tab:results-exp1}
    \vskip 0.12in
    \begin{tabular}{rcc}
      \hline
      & $P(common)$ & $P(rare)$ \\
      \hline
      A & 0.69 & 0.31 \\
      AB & 0.94 & 0.06 \\
      AC & 0.08 & 0.92 \\
      B & 0.94 & 0.06 \\
      \textbf{BC} & \textbf{0.33} & \textbf{0.67} \\
      C & 0.04 & 0.96 \\
    \end{tabular}
  \end{center}
\end{table}

@@

In this experiment, we implemented the IBRE in a way most similar to cued-recall memory tasks.
Previous category labels were treated as features.
And features were selected to be solid black geometric shapes.
The task asked participants to memorise the arrangement of these shapes.
On each trial, we randomised the position of the geometric shapes in the arrangement.
This further minimised the chances of having any design component suggestive of which feature is the category label.

@@

\begin{figure}
  \begin{center}
    \caption{Simple geometric shapes used as stimuli in Experiment 2.}
    \label{figure:exp2-stimuli}
    \includegraphics[scale=0.15]{figures/experiment_2_stimuli.pdf}
  \end{center}
\end{figure}

@@

I have a myriads of things to say here. \\

\subsubsection*{Analysis and Exclusion}

We applied the same analysis and exclusion methods as in Experiment 1.

@@

After exclusion, 30 participants made it into our analysis.
The group-level mean probabilities are shown on Table \ref{tab:results-exp2}.
The resuls are a qualitative and ordinal match to Experiment 1.
Participants showed a clear common preference for stimuli A, $M_{A} = 0.21$, 95\% HDI $[0.11, 0.31]$, $\mathrm{BF}_{10} = 11,312.94$.

\begin{table}[H]
  \begin{center}
    \caption{Group-level mean probabilities for each stimulus
    presented during the test phase in Experiment 2 after exclusion.\\}
    \label{tab:results-exp2}
    \vskip 0.12in
    \begin{tabular}{rcc}
      \hline
       & $P(common)$ & $P(rare)$ \\
      \hline
      A & 0.78 & 0.22  \\
      AB & 0.95 & 0.05 \\
      AC & 0.09 & 0.91 \\
      B & 0.92 & 0.07  \\
      \textbf{BC} & \textbf{0.35} & \textbf{0.65} \\
      C & 0.08 & 0.92 \\
    \end{tabular}
  \end{center}
\end{table}

Participants also showed a reliable rare preference on ambiguous BC trials, $M_{BC} = 0.64$, 95\% HDI $[0.53, 0.75]$, $\mathrm{BF}_{10} = 4.09$
Therefore we conclude that we reliably detected the IBRE.

@@

All things will be free.
